Optimal Task Phasing for End-To-End Latency in Harmonic and Semi-Harmonic Automotive Systems

### 2024-09-26 paper.tex
motivation notation

\section{Motivating Example}

	In this section, we demonstrate the impact of task phasing on the end-to-end latency. 
	To that end, we consider an example cause-effect chain $E = (\tau_1 \to \tau_2 \to \tau_3)$ with: 
	\begin{itemize}
		\item $\tau_1,\tau_3 \in \mathit{Per}(10)$
		\item $\tau_2 \in \mathit{Per}(1)$.
	\end{itemize}
	%
	The typical approach of making the task set synchronous, i.e., $\tau_1, \tau_2, \tau_3 \in \mathit{Phase}(0)$ leads to the schedule depicted in Figure~\ref{fig:motivation:synchronous}.
	%
	\begin{figure}
		\centering
		\subfloat[Synchronous: $\lat(E) = 40$.]{
		\footnotesize
		\begin{tikzpicture}[yscale=0.22, xscale=0.2]

@@

	We observe in Figure~\ref{fig:motivation:synchronous}, that after the write-event of the gray job of $\tau_2$, the next read-event of task $\tau_3$ is time units later. 
	Therefore, by moving the phase of $\tau_3$ from $0$ to $1$, we ensure that the data is read by task $\tau_3$ immediately after it was written by $\tau_2$.
	Specifically, Figure~\ref{fig:motivation:phasing} depicts the case with modified phase $\tau_3 \in \mathit{Phase}(1)$.
	The longest $1$-partitioned job chain has a length of $\ell(\pc^1_1) = 31$.
	Therefore, the end-to-end latency for the case with modified phase is $\lat(E) = 31$.
	We conclude that modifying the phase of $\tau_3$ by only $1$ time unit improved the end-to-end latency by $\frac{9}{40} = 22.5\%$.

>>>>

\section{Motivating Example}
\label{sec:motivation}

	In this section, we demonstrate the impact of task phasing on the end-to-end latency. 
	To that end, we consider an example cause-effect chain $E = (\tau_1 \to \tau_2 \to \tau_3)$ with: 
	\begin{equation}
		T_{\tau_1} = 10, \qquad T_{\tau_2}=1, \qquad T_{\tau_3}=10
	\end{equation}
	% \begin{itemize}
	% 	\item $T_1 = 10$
	% 	\item $T_2 = 1$
	% 	\item $T_3 = 10$
	% \end{itemize}
	%
	The typical approach of making the task set synchronous, i.e., 
	\begin{equation}
		\phi_{\tau_1} = \phi_{\tau_2} = \phi_{\tau_3} = 0 
	\end{equation}
	% $\tau_1, \tau_2, \tau_3 \in \mathit{Phase}(0)$ 
	leads to the schedule depicted in Figure~\ref{fig:motivation:synchronous}.
	%
	\begin{figure}
		\centering
		\subfloat[Synchronous: $\lat(E) = 40$.]{
		\footnotesize
		\begin{tikzpicture}[yscale=0.22, xscale=0.2]

@@

	We observe in Figure~\ref{fig:motivation:synchronous}, that after the write-event of the gray job of $\tau_2$, the next read-event of task $\tau_3$ is time units later. 
	Therefore, by moving the phase of $\tau_3$ from $0$ to $1$, we ensure that the data is read by task $\tau_3$ immediately after it was written by $\tau_2$.
	Specifically, Figure~\ref{fig:motivation:phasing} depicts the case with modified phases:
	\begin{equation}
		\phi_{\tau_1} = \phi_{\tau_2} = 0 , \qquad  \phi_{\tau_3} = 1
	\end{equation} 
	The longest $1$-partitioned job chain has a length of $\ell(\pc^1_1) = 31$.
	Therefore, the end-to-end latency for the case with modified phase is $\lat(E) = 31$.
	We conclude that modifying the phase of $\tau_3$ by only $1$ time unit improved the end-to-end latency by $\frac{9}{40} = 22.5\%$.
